The Role of Video Data Sharing in Advancing Education Policy and Practice

### 2015-05-09 2015-06-01-nsf-ed-workshop/paper.tex
chg acknowledgments to author note and move to front

@@

The Databrary team recognizes that other data repositories enforce strict metadata ontologies and that these Doing may have benefits in sub-domains of research when there is community consensus on core concepts. 
The Databrary team has chosen not to require strict metadata ontologies for several reasons. 
We hope to reduce the pre-deposit curational demands on contributors and foster the rapid adoption of data sharing.Developing and achieving agreement on metadata ontologies can take significant amounts of time. 
Video data are so rich and complex that in many domains, researchers have not settled on standard definitions for particular behaviors and may have little current need for standard tasks, procedures, or terminology. 
However, Databrary empowers users to re-use tags and terminology by suggesting common or similar terms, without confining users to these suggestions. 
User communities within Databrary may eventually converge on common conceptual and metadata ontologies based on the most common (and commonly endorsed) keyword tags, but standardized ontologies are not necessary for browsing and searching in most of the use cases we envision.
The Databrary team believes that the effort spent creating this powerful and flexible system will enable it to be extended to a diverse communities engaged in educational research.

@@

\section{Acknowledgments}

Databrary is based on work supported by the National Science Foundation under Grant No. BCS-1238599, the Eunice Kennedy Shriver National Institute of Child Health and Human Development under Cooperative Agreement U01-HD-076595, and the Society for Research in Child Development.
Any opinions, findings, and conclusions or recommendations expressed in the material contributed here are those of the author(s) and do not necessarily reflect the views of the National Science Foundation, the Eunice Kennedy Shriver National Institute of Child Health and Human Development, or the Society for Research in Child Development.

>>>>

\authornote{Rick O. Gilmore is in the Department of Psychology, The Pennsylvania State University, University Park, PA 16802, rogilmore@psu.edu. Databrary is based on work supported by the National Science Foundation under Grant No. BCS-1238599, the Eunice Kennedy Shriver National Institute of Child Health and Human Development under Cooperative Agreement U01-HD-076595, and the Society for Research in Child Development.
Any opinions, findings, and conclusions or recommendations expressed in the material contributed here are those of the author(s) and do not necessarily reflect the views of the National Science Foundation, the Eunice Kennedy Shriver National Institute of Child Health and Human Development, or the Society for Research in Child Development.}

@@

The Databrary team recognizes that other data repositories enforce strict metadata ontologies and that these Doing may have benefits in sub-domains of research when there is community consensus on core concepts. 
The Databrary team has chosen not to require strict metadata ontologies for several reasons. 
We hope to reduce the pre-deposit curational demands on contributors and foster the rapid adoption of data sharing.Developing and achieving agreement on metadata ontologies can take significant amounts of time. 
Video data are so rich and complex that in many domains, researchers have not settled on standard definitions for particular behaviors and may have little current need for standard tasks, procedures, or terminology. 
However, Databrary empowers users to re-use tags and terminology by suggesting common or similar terms, without confining users to these suggestions. 
User communities within Databrary may eventually converge on common conceptual and metadata ontologies based on the most common (and commonly endorsed) keyword tags, but standardized ontologies are not necessary for browsing and searching in most of the use cases we envision.
Future challenges include building the capacity to searching for tagged segments inside of videos.
Some of within-video tagging functionality exists in the current software, with more extensive search and preview capabilities on the near horizon.

The Databrary team believes that the effort spent creating this powerful and flexible system will enable it to be extended to a diverse communities engaged in educational research.

@@
